\LARGE{Approximate Code: A Cost-Effective Erasure Code for MultimediavApplications in Cloud Storage Systems}\\

### 2019-03-27 paper.tex
version 0.3.2.1

In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks, we use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows.
Our design assumes that the parameters  $(n, m, s,t)$ are user-defined configurable parameters so the constructor of the Approximate Code will be determined by these 4 parameters.
For convenience, we label $h=n-m-s$ as the number of columns of important data.
We choose the value of $r$ according to equation $r=s+h$, which will be explained in \ref{Data Distribution}.
Figure \ref{apcode-7222-v2} shows an example of Approximate Codes with $n = 7$,$m = 2$ , $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.

@@

\subsubsection{Encoding Process}
We explain the encoding process through Figure \ref{apcode-7222-v2}, which shows the two encoding phases of Approximate Codes.

\textbf{Phase 1:} Encode important data sectors based on Galois Field (GF). Phase 1 generate $s$ groups of RS parity sectors labeled with $q_{i,j}$ and they are defined by equation \ref{q_ij}, where $\alpha$ is the coefficient in GF. 
For example, $q_{0,0} = \alpha_0 d_{0,0} + \alpha_1 d_{0,1} + \alpha_2 d_{0,2}$ and 
$q_{1,1} = \alpha_0^2 d_{1,0} + \alpha_1^2 d_{1,1} + \alpha_2^2 d_{1,2}$

>>>>

In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks, we use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows.
Our design assumes that the parameters  $(n, m, s,t)$ are configurable parameters shus the constructor of the Approximate Code will be determined by these 4 parameters.
Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$.
The relevant instructions will be shown in \ref{Data Distribution}.
Meanwhile, we label $h=n-m-s$ as the number of columns of important data for convenience.

Figure \ref{apcode-7222-v2} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.

@@

\subsubsection{Encoding Process}
The encoding process can be divided into two phases: important coding phase and global coding phase. We us RS code to generate both important parity sectors and global parity sectors.

\emph{Phase 1} Encode important data sectors based on Galois Field (GF) and generate $s$ groups of RS parity sectors labeled with $q_{i,j}$ and they are defined by equation \ref{q_ij}, where $\alpha$ is the coefficient in GF. According to Figure \ref{apcode-7222-v2}, Phase 1 use RS(5,3).
For example, $q_{1,1} = \alpha_0^2 d_{1,0} + \alpha_1^2 d_{1,1} + \alpha_2^2 d_{1,2}$
